
```{r}
pacman::p_load(tidyverse, meta)
```

Oberg 1993 Table 8a.
```{r}
SL.men = tibble(
   sex = "Male",
   age.cat = c('10-14','15-19','20-29','30-39','40-49','50-59','60-69','70-79'),
   age.mid = c(12.5,17.5,25,35,45,55,65,75),
   N = c(12,15,15,15,15,15,15,14),
   mean.cm = c(61.5, 66.0, 61.6, 64.9, 64.7, 63.5, 65.0, 61.5),
   SD.cm = c(3.9, 4.8, 3.5, 4.6, 3.7, 6.0, 3.6, 5.1),
) 

SL.women = tibble(
   sex = "Female",
   age.cat = c('10-14','15-19','20-29','30-39','40-49','50-59','60-69','70-79'),
   age.mid = c(12.5,17.5,25,35,45,55,65,75),
   N = c(12,15,15,15,15,15,15,15),
   mean.cm = c(54.2, 59.3, 59.1, 59.7, 57.1, 53.5, 55.3, 54.2),
   SD.cm = c(2.9, 4.3, 6.3, 5.3, 3.7, 2.6, 4.2, 3.7)
) 

SL = bind_rows(SL.men, SL.women) %>%
  mutate(CV = SD.cm / mean.cm) %>%
   filter(age.mid > 30) 

SL
```


Get regression model to smooth estimates across ages
```{r}
lm = lm(mean.cm ~ age.mid * sex, data=SL)
summary(lm)
```

Or, better yet, using meta-regression
```{r}
meta = metagen(TE=mean.cm, seTE=SD.cm/sqrt(N), data=SL)
metareg(meta, ~age.mid*sex)
```

Equation for normative SL based on age and sex:

$62.3704 - 0.1202*age + 4.8810(if.male) + 0.0621*age (if.male)$

Or, can use separate equations for women/men:
   Women:   62.3704 - 0.1202*age
   Men:     67.2514 - 0.0581*age

Plot for mean SL
```{r}
ggplot(data=SL, mapping=aes(x=age.mid, y=mean.cm, ymin=mean.cm-SD.cm, ymax=mean.cm+SD.cm, group=sex, color=sex)) +
   geom_errorbar() +
   scale_color_manual(values=c("red","blue")) +
   geom_abline(intercept=62.3704, slope=-0.1202, col="red", lwd=2, lty=2) +
   geom_abline(intercept=67.2514, slope=-0.0581, col="blue", lwd=2, lty=2) +
   theme_bw(base_size=14) +
   labs(x="Age (years)", y="Mean Step Length (cm)")
```



Meta-analysis for SD (actually for variance)
```{r}
meta.varSL = metagen(TE=SD.cm^2, seTE=SD.cm^2 * sqrt(2/(N-1)), data=SL)
meta.varSL
metareg(meta.varSL, ~ age.mid * sex) # no effect of age or sex
metareg(meta.varSL, ~ mean.cm) # possible higher variability with higher mean values - let's calculate CV instead
```

Plot for SD SL
```{r}
ggplot(data=SL, mapping=aes(x=mean.cm, y=SD.cm^2, col=sex, ymin=SD.cm^2-SD.cm^2 * sqrt(2/(N-1)), ymax=SD.cm^2+SD.cm^2 * sqrt(2/(N-1)))) +
   geom_errorbar() + geom_point() +
   scale_color_manual(values=c("red","blue")) +
   geom_abline(intercept=-24.4196, slope=0.6537, col="purple", lwd=2, lty=2) +
   theme_bw(base_size=14) +
   labs(x="Mean Step Length (cm)", y="Variance in Step Length (cm^2)")
```


```{r}
meta.CV.SL = metagen(TE=CV, seTE=sqrt( CV^2 / (N-1) * (0.5 + CV^2 ) ), data=SL)
metareg(meta.CV.SL, ~ age.mid * sex) # no effect of age or sex
meta.CV.SL
```

Plot for CV SL
```{r}
ggplot(data=SL, mapping=aes(x=age.mid, y=CV, 
                            ymin=CV - sqrt( CV^2 / (N-1) * (0.5 + CV^2 ) ), 
                            ymax=CV + sqrt( CV^2 / (N-1) * (0.5 + CV^2 ) ), 
                            group=sex, color=sex)) +
  geom_hline(yintercept=0.0662, lwd=2, lty=2) + 
  geom_errorbar(position=position_dodge(width=3), width=3) + 
  geom_point(position=position_dodge(width=3)) +
  scale_color_manual(values=c("red","blue")) +
  theme_bw(base_size=14) +
  labs(x="Age (years)", y="CV Step Length")
```

# Use CV to calculate SD
Since between study variability (I2) is lower for CV vs. SD, and SD seems to increase with the mean (not quite significant but under-powered).

CV does not appear to be influenced by age or sex


# Final formulas

Neurotypical step length:
  Women:   62.3704 - 0.1202*age
  Men:     67.2514 - 0.0581*age

CV in neurotypical step length = 6.62%
SD in neurotypical step length = expected step length x 0.0662

Low step length = 
  lower than the 2.5th percentile of neurotypical step length = 
  lower than mean neurotypical step length - 1.96 SDs 
  
